Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-08-26 paper/paper.Rmd
don't cache chunks loading packages from @bisaloo review

```{r packages}
library(data.table)
library(purrr)
library(scoringutils)
library(lubridate)
library(forcats)
library(ggplot2)
library(ggridges)
library(patchwork)
library(scales)
library(here)
```

>>>>

```{r packages, cache = FALSE}
library(data.table)
library(purrr)
library(scoringutils)
library(lubridate)
library(forcats)
library(ggplot2)
library(ggridges)
library(patchwork)
library(scales)
library(here)
```
